\documentclass[10pt]{article}
\usepackage[document]{ragged2e}
\usepackage{multicol}
\usepackage[margin=1in]{geometry}
\usepackage{titlesec}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot[R]{P. \thepage}
\fancypagestyle{plain}{
    \renewcommand{\headrulewidth}{0pt}
    \fancyhf{}
    \fancyfoot[R]{P. \thepage}
}

\setlength{\parindent}{0em}
\setlength{\parskip}{1em}
\titlespacing*{\section}
{0pt}{0.5em}{0.5em}

\title{Checkpoint 1: SQL Analytics Findings}
\author{The Freedom Deer: Tianchang Li, Hualiang Qin, Qingwei Lan}

\begin{document}
\maketitle

The main goal of our research is to investigate the conditions under which police officers tend to use force on civilians. Specifically we believe that race and environmental conditions play a critical role in this, therefore in this report, we utilized SQL to analyze and answer some important questions.

The questions are split into sections and each section contains multiple questions.

Note that all \texttt{.sql} files can be run with \texttt{psql cpdb cpdb < filename.sql}.

\section*{1. Information about Victims and Officers}

We would like to first gather some information about the officers and victims in the use of force cases. The data in this section is taken from the \texttt{trr\_trr} and \texttt{data\_officer} datasets.

\subsubsection*{1a. What is the racial distribution of the victims involved in cases of use of force?}

SQL file: \texttt{1a.sql}

Results:

\begin{verbatim}
          subject_race          | count
--------------------------------+-------
 Black                          | 49747
 Hispanic                       |  9369
 White                          |  6540
 Asian/Pacific Islander         |   431
 Native American/Alaskan Native |    54
\end{verbatim}

From the results, we can see the race distribution of the subjects involved in use of force cases. As we can see, black subjects are most common.


\subsubsection*{1b. What is the racial distribution of police officers involved in these cases?}

SQL file: \texttt{1b.sql}

Results:

\begin{verbatim}
           officer_race         | count
--------------------------------+-------
 White                          | 38731
 Hispanic                       | 15064
 Black                          | 10599
 Asian/Pacific                  |  2028
 Native American/Alaskan Native |   310
\end{verbatim}

From the results, we can see the race distribution of police officers involved in use of force cases. At the top is white police officers.


\subsubsection*{1c. What portion of the total use of force cases involves an officer that is of a different race than that of the victim (cross-race use of force)?}

SQL file: \texttt{1c.sql}

Results:

\begin{verbatim}
 cross_race_percentage
-----------------------
              0.732046
\end{verbatim}

Based on the results, we can see that cross-race use of force cases make up 73.2\% of total use of force cases.


\subsubsection*{1d. What portion of the cases in use of force cases contained firearm usage.}

SQL file: \texttt{1d.sql}

Results:

\begin{verbatim}
 firearm_used_percentage
-------------------------
                  0.0153
\end{verbatim}

Based on the results, we can see that only 1.5\% use of force cases involved the usage of firearms.


\subsubsection*{1e. What are the percentages of use of force cases grouped by officer race and subject race? (i.e. what is the percentage of white officers using force on black subjects)}

SQL file: \texttt{1e.sql}

Results:

\begin{verbatim}
 percentage |          officer_race          |          subject_race
------------+--------------------------------+--------------------------------
   0.416733 | White                          | Black
   0.157269 | Hispanic                       | Black
   0.141796 | Black                          | Black
   0.083096 | White                          | Hispanic
   0.065161 | White                          | White
   0.043256 | Hispanic                       | Hispanic
   0.020457 | Hispanic                       | White
   0.019950 | Asian/Pacific Islander         | Black
   0.008147 | White                          |
   0.006923 | Black                          | White
   0.006849 | Black                          | Hispanic
   0.005536 | Asian/Pacific Islander         | Hispanic
   0.004238 | White                          | Asian/Pacific Islander
   0.003969 | Asian/Pacific Islander         | White
   0.003357 | Native American/Alaskan Native | Black
   0.002552 | Hispanic                       |
   0.001805 | Black                          |
   0.001044 | Hispanic                       | Asian/Pacific Islander
   0.000731 | Black                          | Asian/Pacific Islander
   0.000627 | Native American/Alaskan Native | Hispanic
   0.000537 | White                          | Native American/Alaskan Native
   0.000463 | Native American/Alaskan Native | White
   0.000418 | Asian/Pacific Islander         | Asian/Pacific Islander
   0.000358 | Asian/Pacific Islander         |
   0.000194 | Hispanic                       | Native American/Alaskan Native
   0.000179 | Native American/Alaskan Native |
   0.000045 | Black                          | Native American/Alaskan Native
   0.000030 | Asian/Pacific Islander         | Native American/Alaskan Native
\end{verbatim}

The results give us a high level overview of the racial distribution of both subjects and police officers in all the use of force cases. A cursive scan shows us that 41\% of all cases come from white police officers' use of force on black subjects. Further analysis shows that cases with black subjects make up 71.58\% of all use of force cases.


\end{document}
